Extrae.jl: Julia bindings for the Extrae HPC Profiler

### 2025-04-16 paper/paper.tex
last paper fixes
try fix symbol clash
Try avoiding svg package and manually include generated TeX code
Fix width of SVG figure
Fix undefined `\svgwidth` length
Rename plots

\begin{figure}[h]
    \centering
    \includegraphics[width=\linewidth]{Instantaneous_parallelism@trace-16-10ms.png}
    \caption{Instantaneous parallelism during the workload of the application measured as the number of MPI ranks not being idle at the given moment. Maximum value is 16 and minimum is 1.}
    \label{fig:parallelism}
\end{figure}

@@

\begin{figure}[h]
    \centering
    \begin{subfigure}{\linewidth}
        \includegraphics[width=\linewidth]{MPI_call@trace-16-10ms.png}
        \caption{Original}
        \label{fig:timeline:orig}
    \end{subfigure}
    \\\vspace{1em}
    \begin{subfigure}{\linewidth}
        \includegraphics[width=\linewidth]{MPI_call@trace-16-10ms-zoom.png}
        \caption{Zoom}
        \label{fig:timeline:zoom}
    \end{subfigure}
    \\\vspace{1em}
    \caption{Timeline of MPI calls for the (a) runtime of the application and (b) zoom on 
 a couple of iterations of the main workload. Horizontal axis is time and each row shows the events that took place on each MPI rank. Blocks represent MPI calls where color maps to MPI routines and the start and end positions fit the duration of the call. Yellow lines represent messages sent betweens ranks.}
    \label{fig:timeline}
\end{figure}

@@

\begin{figure}[h]
    \centering
    \includegraphics[width=.8\linewidth]{paper/assets/2D_-_connectivity@trace-16-10ms.png}
    \caption{Connectivity pattern between MPI ranks measured as the number of messages sent from MPI rank \textit{x} to rank \textit{y}. Grey cells mean no communication while green cells mean represent a value of 2,016 messages sent.}
    \label{fig:connectivity}
\end{figure}

@@

\begin{figure}
    \centering
    \includegraphics[width=\linewidth]{Node_bandwidth_(MB_s)@trace-16-10ms.w_legend.png}
    \caption{Node network bandwidth in the time region of Figure~\ref{fig:timeline:zoom} measured in MB/s. Only one node is shown because all MPI ranks run on the same node.}
    \label{fig:node-bw}
\end{figure}

>>>>

\begin{figure}[h]
    \centering
    \includegraphics[width=\linewidth]{Instantaneous_parallelism-trace-16-10ms.png}
    \caption{Instantaneous parallelism during the workload of the application measured as the number of MPI ranks not being idle at the given moment. Maximum value is 16 and minimum is 1.}
    \label{fig:parallelism}
\end{figure}

@@

\begin{figure}[h]
    \centering
    \begin{subfigure}{\linewidth}
        \includegraphics[width=\linewidth]{MPI_call-trace-16-10ms.png}
        \caption{Original}
        \label{fig:timeline:orig}
    \end{subfigure}
    \\\vspace{1em}
    \begin{subfigure}{\linewidth}
        \includegraphics[width=\linewidth]{MPI_call-trace-16-10ms-zoom.png}
        \caption{Zoom}
        \label{fig:timeline:zoom}
    \end{subfigure}
    \\\vspace{1em}
    \caption{Timeline of MPI calls for the (a) runtime of the application and (b) zoom on 
 a couple of iterations of the main workload. Horizontal axis is time and each row shows the events that took place on each MPI rank. Blocks represent MPI calls where color maps to MPI routines and the start and end positions fit the duration of the call. Yellow lines represent messages sent betweens ranks.}
    \label{fig:timeline}
\end{figure}

@@

\begin{figure}[h]
    \centering
    \includegraphics[width=.8\linewidth]{paper/assets/2D_-_connectivity-trace-16-10ms.png}
    \caption{Connectivity pattern between MPI ranks measured as the number of messages sent from MPI rank \textit{x} to rank \textit{y}. Grey cells mean no communication while green cells mean represent a value of 2,016 messages sent.}
    \label{fig:connectivity}
\end{figure}

@@

\begin{figure}
    \centering
    \includegraphics[width=\linewidth]{Node_bandwidth_MB_s-trace-16-10ms.w_legend.png}
    \caption{Node network bandwidth in the time region of Figure~\ref{fig:timeline:zoom} measured in MB/s. Only one node is shown because all MPI ranks run on the same node.}
    \label{fig:node-bw}
\end{figure}
